Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-05 manuscript.Rmd
Uncited plot functional.

# Plotting function    
ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
    facet_wrap(~ Abbrev) + 
    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99") + 
    theme_bw() +
    theme(legend.position = "bottom", 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
    ylim(c(0,225)) +
    scale_x_continuous(breaks=seq(1989, 2020, 8))

@@

```{r plotScatter}

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n = n()) %>%
    arrange(title)

H <- unique.titles$Hodge

final.list <- cbind(n.so.yr, H)
final.list <- arrange(final.list, desc(n))
final.list.index <- full_join(final.list, hIndex, by = "title")

final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
#    theme_bw() 
final.list.index$scaleScore <- scale(final.list.index$n)
final.list.index$hScaled <- scale(final.list.index$h5Index)
final.list.index <- arrange(final.list.index, scaleScore)

x <- ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
    xlim(c(-3, 3))

>>>>

# Plotting function    
plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
    facet_wrap(~ Abbrev) + 
    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
    theme_bw() +
    theme(legend.position = "bottom", 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
    ylim(c(0,225)) +
    scale_x_continuous(breaks=seq(1989, 2020, 8))

@@

```{r uncitedSummary}
#=======================================
# Create new data file 
#=======================================

articles.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title) %>%
    rename(Year = year, Journal= title)

scopus.df <- read.csv("scopus.csv")
articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))

articles.df<- articles.df %>% 
    filter(Year <= 2013) %>%
    mutate(propNotCited = X..Not.Cited/100) %>%
    select(-X, -SJR, -SNIP, -Citations, -IPP, -X..Not.Cited, -Overall.N, -X..Review) %>%
    rename(HD.N = N, scopus.N = Documents)

#=======================================
# Calculate number of uncited articles
#=======================================

#  First reduce the data file to 1996 to 2010. Data contained significant problems that brought the number of uncited values to almost 0.  Was not reliable.

df.96.10 <- filter(articles.df, Year >= 1996, Year <= 2010)

# If HD article count is missing, replace with Scopus count
df.96.10$HD.N <- ifelse(is.na(df.96.10$HD.N), df.96.10$scopus.N, df.96.10$HD.N)

# Some counts have 0 values.  Set these to NA and then omit
df.96.10$HD.N <-ifelse(df.96.10$HD.N == 0, NA, df.96.10$HD.N) 
df.96.10 <- df.96.10[!is.na(df.96.10$HD.N), ]

# If uncited proportion is missing, compute average for that particular journal
# Replace missing value with the mean value
df.96.10 <- df.96.10 %>% group_by(Journal) %>%
        mutate(meanPropUncited = mean(propNotCited, na.rm=TRUE)) %>% ungroup()

df.96.10$propNotCited <- ifelse(is.na(df.96.10$propNotCited),
     df.96.10$meanPropUncited, df.96.10$propNotCited)

# If uncited proportion is missing because it was not in scopus, replace the missing
# value with the overall mean uncited proportion

overallPropUncited <- mean(df.96.10$propNotCited, na.rm=TRUE)

df.96.10$propNotCited <- ifelse(is.na(df.96.10$propNotCited), overallPropUncited, df.96.10$propNotCited)

# Calculate number of not cited

df.96.10 <- df.96.10 %>% mutate(countNotCited = HD.N - (HD.N * propNotCited))

df.96.10.Summary <- df.96.10 %>% group_by(Year) %>%
    summarize(Published = sum(HD.N), 
              Uncited = sum(countNotCited))

#============================================
# Create a melted data frame for the plot
#============================================

df.95.11 <- select(articles.df, Year, HD.N) %>% 
    filter(Year <= 1995 |Year >=2011) %>%
    rename(published = HD.N) %>%
    group_by(Year) %>%
    summarize(Published = sum(published, na.rm=TRUE)) %>%
    ungroup() %>%
    mutate(Uncited = NA)

uncited.df <- rbind(df.96.10.Summary, df.95.11) %>%
    arrange(Year)
uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100    
uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited")], id.vars = "Year")

#=======================================
# Create text annotations to plot 
#=======================================

percent.df <- uncited.df
percent.df$percentage <- round(percent.df$percentage, digits=1) 
percent.df$percentLabel<- paste(percent.df$percentage, "%", sep="")
percent.df <- na.omit(percent.df)
percent.df <- percent.df[c(seq(1, 15, 3), 15),]

#=======================================
# Create the plot 
#=======================================

cp <- c("#5e3c99", "#e66101")

ggplot(observed.df.melted, aes(Year, value, colour = variable)) + 
    geom_line(alpha = .60) + 
    geom_point(size =4) +
    scale_color_manual(values=cp, labels = c("Number of Articles Published",
         "Estimated Number of Uncited Articles")) +
    theme(legend.title=element_blank()) +
    theme(legend.position = "bottom") +
    ylab("N") +
    geom_text(data = percent.df, aes(Year, Uncited -70, label = percentLabel), size =4, colour = "black") +
    scale_y_continuous(breaks = seq(0, 2250, 250), limits = c(0, 2250))
